\chapter{Basic philosophical commitments}
\label{chap:basic-comm}
I want to start this essay by setting out some basic features of my approach to
moral philosophy.
One of the most important features of my approach is a form of pragmatic pluralism
about both ontology and ethics.
The gist of this position is that the world itself does not fully determine either
a singular true portrayal of the world, or a single correct set of ethical
beliefs.
Human beings construct their understandings of the world and their ethical views
through active engagement with the world.
This process is shaped both by deep features of the world itself and by the
culture, practices, aims, and history of the community and individuals that are
seeking to understand the world or to make sound ethical judgments.
Consequently, I think that different communities might come to understand the
world, in very different ways, and nonetheless have views that reflect deep
features of the world and serve the purposes for which they are seeking to
understand the world.
Likewise, I think that different communities or individuals might come to adopt
very different sets of ethical beliefs and practices which all reflect deep
ethical truths and all constitute sound ethical practice.
This implies that there may be more than one correct, (or at least reasonable)
understanding of the world, and that their may be more than one sound set of
ethical beliefs and practices.
It does not imply, however, that all beliefs about the world or all sets of
ethical belief and practice are equally valid or reasonable.
Some models of the world are more accurate or more useful than others, and some
sets of ethical belief and practice are more consistent with deep ethical truths
than others.

I will explain these positions in more detail in the following sections.
First I will explain the particular flavor of ontological pluralism that informs
my ethics and metaethics in \refse{sec:ont_plural}.
After this I will explain how I understand moral reasoning, in
\refse{sec:nat_mor}. This will enable me to defend a form of ethical and
metaethical pluralism in \refse{sec:eth_plur}.
\section{Ontological pluralism}
\label{sec:ont_plural}
There is no uniquely correct way to understand the world.
When we seek to understand the world, we use concepts that we have inherited
from others or we develop our own by interacting in the world and sometimes, to
shape it to our purposes.
These concepts give us ways to understand and interact with the world
effectively.
We use these concepts to model the world and to chop it into manageable bits
that we can understand.
So, for instance, when I look at the corner my desk, I do not simply see a
series of meaningless shapes and colors; I see a lamp and a pine cone that I
put there to make my space feel warm and inviting.
\emph{Lamp}, \emph{pine cone}, and \emph{desk} are useful concepts for me because they
provide a meaningful way for me to model and interact with my world.
These categories reflect both features of the objects themselves and ways that
human beings tend to interact with them.
It is useful to think of lamps, pine cones, and desks both as wholes and as
distinct and persistent physical objects, because I interact with them as
distinct and persistent physical objects.
These concepts also constitute meaningful categories because they reflect
important, recognizable patterns in my world (many trees in the pacific
northwest produce seed-bearing cones), or they reflect ways in which people
regularly interact with objects in my world (people make lamps and desks and
use them to light their rooms or to write essays on).

This suggests that, assuming that human beings are a part of a real world and
interact with this world, concepts are shaped both by human cultures and by deep
features of reality itself.
Both of these facts are important.
On the basis of these assumptions, we can assert that both concepts and truth
claims are conventional in the broad sense that they depend on certain linguistic
conventions.
But we can also assert that these concepts and truth claims are not entirely
arbitrary.
In forming concepts, human beings make choices, but these choices are not
entirely arbitrary.
\section{On the nature of morality and moral reasoning}
\label{sec:nat_mor}
\section{Ethical and metaethical pluralism}
\label{sec:eth_plur}
There are at least four basic philosophical commitments that inform my approach.

I want to answer the question, what are we doing when we are doing moral
philosophy.
\chapter{Foundational ethical commitments}
\label{ch:eth_com}
