\chapter{Social and legal relationships}
\label{cha:soci-legal-relat}
One of the key aims of this project is to examine the structures of power and
obligation that are created or presupposed by the institution of private property.
In this chapter, I will set out some of the analytical tools that I use to do
this.
Specifically, I will provide some vocabulary for discussing two types of
phenomena:

\begin{enumerate}
\item Relationships of obligation and accountability.

\item The power to transform such relationships.
\end{enumerate}

These two sorts of phenomena play key roles in shaping the normative terrain of a
society.

I borrow some of these tools from W. N. Hohfeld's, seminal two-part essay, \emph{Some
fundamental legal relations in judicial reasoning}
\citeyearpar{hohfeldfundamentallegal1913,hohfeldfundamentallegal1917}.
In this essay Hohfeld sets out several basic legal relationships and defines them
in terms of one another \citeyearpar[pp.
  28–59]{hohfeldfundamentallegal1913}

Hohfeld's analytical tools are best suited to examining legal systems, and moral
systems and social arrangements that mirror the normative structure of legal
systems.

As I said, in Chapter 1, there are many ways to model and conceive of moral and
social relationships.
\section{Duties and claims}
\label{sec:duties-claims}
A central feature of moral life in communities is the notion that there are
certain things that we owe to one another, and certain things that other people
can claim from us as their due.
This generally, is what we speak about when we talk about duties and claims.
Philosophers often argue about what precisely what features are necessary for
duties.
\subsection{Relationships of obligation and accountability}
\label{sec:obl-acc}
There are many ways to model these relationships.
Philosophers
\section{Legal powers}
\label{sec:legal-powers}
\begin{quote}
A change in a given legal relation may result (1) from some superadded fact or
group of facts not under the volitional control of a human being (or human
beings); or (2) from some superadded fact or group of facts which are under the
volitional control of one or more human beings.
As regards the second class of cases, the person (or persons) whose volitional
control is paramount may be said to have the (legal) power to effect the
particular change of legal relations that is involved in the problem.
\citep[p.
   44]{hohfeldfundamentallegal1913}
\end{quote}
\section{Formal tools}
\label{sec:formal-tools}
\subsection{Hohfeld's taxonomy of basic legal relationships}
\label{sec:hohf-taxon}
In his seminal two part essay, , W. N. Hohfeld
\citeyearpar{hohfeldfundamentallegal1913,hohfeldfundamentallegal1917} sets
out to provide precise definitions of several basic legal concepts, as an
antidote for what he sees and sloppy legal reasoning.
In the first of these essays, he defines two sets of four types of legal relationships in terms
of their logical relationships with one another.
These definitions provide a helpful way to examine the formal structure of legal
systems and other moral and social arrangements.

Hohfeld's first tetrad of legal relationships can be used to model the legal
duties that persons owe one another under specific legal systems.
It is organized around the idea of a legal duty that one person has to another
person to perform or omit some action.
According to Hohfeld's taxonomy, this duty corresponds to a claim that the
latter bears against the former.
Specifically, the claim that the former perform or omit the relevant
action.\footnote{Hohfeld called these legal claims, \emph{rights}, and he used the term \emph{right}
exclusively for this sort of legal relationship.
Common usage supports using the term \emph{right} much more broadly, so I prefer to use
the term or \emph{claim right} or simply \emph{claim} to refer to this more specific type of
legal relationship.}
So if, for instance, Sarandon has a legal duty to Davis not to drive Davis off of
a cliff, then Davis has a claim against Sarandon, that Sarandon not drive heroff
of a cliff.
However, if Sarandon has no legal duty to Davis not to drive Davis off of a
cliff, then Davis has no legal claim against Sarandon that Sarandon not drive
her off of a cliff.
\emph{The liberty to perform some action is not limited to those c}

More formally, given any two persons, \emph{A} and \emph{B}, and any action or omission,
\(\phi\): \[\begin{aligned} \text{\emph{A} has a duty to \emph{B} to }\phi\:
    \veebar\: \text{\emph{A} has no duty to \emph{B} to }\phi.
    \\ \text{\emph{B} has a claim on \emph{A} that \emph{A} }\phi{}\: \veebar\:
    \text{\emph{B} has no claim on \emph{A} that \emph{A} }\phi{}.
    \\ \text{\emph{A} has a duty to \emph{B} to }\phi \iff \text{\emph{B} has a
    claim on \emph{A} that \emph{A} }\phi.
    \\ \text{\emph{A} has no duty to \emph{B} to }\phi \iff \text{ \emph{B} has no
    claim on \emph{A} that \emph{A} }\phi.
    \end{aligned}\]

This consists of these four legal relationships:

\begin{description}
\item[{Duty}] A duty to another person to perform (or omit) a particular action.

\item[{Claim}] A claim against another person that they perform (or omit) a
particular action.

\item[{No duty}] No duty to another person to perform (or omit) a particular action.

\item[{No claim}] No claim against another person that they perform or omit a
particular action.
\end{description}

Hohfeld and many of those who have adopted his basic taxonomy of legal
relationships, have given these legal relationships special names.
These names are often confusing, because, in ordinary legal parlance, they carry
implications that do not hold under Hohfeld's, rather minimal, definitions of
these terms.

(A has a duty to B to \(\phi\)).
(B has a claim against A that A \(\phi\))
